\documentclass[12pt,a4paper]{article}

% ----------------------------
% Packages
% ----------------------------
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{datetime2}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{rotating}
\usepackage{acronym} 
\usepackage{subcaption}

% ----------------------------
% Formatting
% ----------------------------
\setstretch{1.2}
\setlength{\parskip}{0.6em}
\setlength{\parindent}{0pt}

\titleformat{\section}
    {\normalfont\Large\bfseries}
    {\thesection}{1em}{}

\titleformat{\subsection}
    {\normalfont\large\bfseries}
    {\thesubsection}{1em}{}

% ----------------------------
% Header / Footer
% ----------------------------
\setlength{\headheight}{15pt}  
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textit{Quantum Imaging with Undetected Photons}}
\fancyhead[R]{\leftmark}
\fancyfoot[C]{\thepage}

% ----------------------------
% Document Metadata
% ----------------------------
\title{Quantum Imaging with Undetected Photons: Enhanced Image Processing \& User Interface}
\author{Samer Saftawi}
\date{February 2026}

% ----------------------------
% Document
% ----------------------------
\begin{document}

\begin{titlepage}
\centering

\vspace*{2cm}

{\Large\bfseries Thesis Report -- Graduation Internship\par}
\vspace{1.2cm}

{\Huge\bfseries Quantum Imaging with Undetected Photons: Enhanced Image processing \& User Interface\par}

\vspace{4cm}

{\large
\begin{tabular}{@{}l l@{}}
\textbf{Author:} & Samer Saftawi \\
\textbf{Study program:} & Bach

elor Applied Computer Science \\
\textbf{Student number:} & 541642 \\
\end{tabular}
}

\vspace{1.5cm}

{\large
\begin{tabular}{@{}l l@{}}
\textbf{Supervisor:} & Dr. D. Polishchuk \\
\textbf{Study Coach:} & Dr. A. Khan \\
\textbf{Research group:} & Applied Nanotechnology \\
\textbf{Project:} & Quantum Delta NL \\
\textbf{Institution:} & Saxion University of Applied Sciences \\
\end{tabular}
}

\vfill

{\large
Internship period: 02.02.2026 -- 03.07.2026\\
}

\end{titlepage}

\newpage
\section*{Foreword}
As a student at Saxion -- University of Applied Sciences, this project will be a graduation internship that serves as the final step in completing the Bachelor of Applied Computer Science program.

Quantum Photonics is an emerging field that explores the quantum properties of light and their applications in various technologies, including quantum imaging. \ac{QIUP} is an advanced technique that allows for imaging objects without directly detecting the photons that interact with them, leveraging quantum entanglement and interference effects.

The \ac{ANT} research group at Saxion is actively involved in advancing quantum photonics technologies, including \ac{QIUP}. This project will focus on enhancing the image processing and developing a user-friendly interface for the \ac{QIUP} system, aiming to improve the quality of the images produced and make the technology more accessible to researchers and practitioners in the field.

\newpage
\section*{Summary}
The aim of this report is to make Quantum technologies more accessible to a wider audience by contributing to the advancement of quantum imaging technology.
\ac{FFT}, an advanced image processing method, was used to enhance the quality of images produced by \ac{QIUP}.
Additionally, a user-friendly interface was developed to allow researchers and practitioners to easily interact with the \ac{QIUP} system, facilitating the adoption and application of this cutting-edge technology in various fields.

\textbf{--- TO DO ---:} Results, Conclusions, and Recommendations.

\newpage
\tableofcontents

\newpage
\section*{Abbreviations}
\markboth{LIST OF ABBREVIATIONS}{List of Abbreviations} 
\begin{acronym}[]
    \acro{QIUP}{Quantum Imaging with Undetected Photons}
    \acro{ANT}{Applied Nanotechnology}
    \acro{FFT}{Fast Fourier Transform}
\end{acronym}


\newpage
\section*{List of Figures and Tables}

\newpage
\section{Introduction}

\subsection{Background of the Assignment}

\subsection{Problem Definition and Objectives}

\subsection{Scope of Work}

\subsection{Approach \& Methodology}

\subsection{Outline of the Report}
\begin{enumerate}
    \item \textbf{Introduction} -- Provides background on quantum imaging technology, defines the problem statement, outlines project objectives, and presents the methodology and scope of work.
    
    \item \textbf{Analyse/Specifications} -- Details the requirements analysis, system specifications, and constraints for the enhanced image processing and user interface development.
    
    \item \textbf{Functional Design} -- Describes the functional architecture, user workflows, and feature specifications for the image processing algorithms and UI components.
    
    \item \textbf{Technical Design} -- Presents the technical implementation approach, software architecture, technology stack, and design patterns used for the project.
    
    \item \textbf{Realisation} -- Documents the actual implementation of the system, including code development, integration, and deployment of the quantum imaging software.
    
    \item \textbf{Testing} -- Covers testing strategies, test cases, results, and validation of the image processing quality and user interface functionality.
    
    \item \textbf{Conclusions and Recommendations} -- Summarizes key findings, evaluates achievement of objectives, and provides recommendations for future improvements and research directions.
\end{enumerate}

\newpage
\section{Analyse / Specifications}

\newpage
\section{Functional Design}

\newpage
\section{Technical Design}

\newpage
\section{Realisation}

\newpage
\section{Testing}

\newpage
\section{Conclusions and Recommendations}

\subsection{Conclusions}

\subsection{Recommendations}

\newpage
\section*{References}

\newpage
\section*{Appendices}

\end{document}